---
title: "Social Cost of Carbon and Policy Choice Under Uncertainty- ESM 204 Assignment 4"
author: "Abigail Sanford"
date: "May 27th, 2022"
output:
  html_document:
    code_folding: hide
---

```{r setup, include = TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(rootSolve)
library(janitor)
library(here)
```


```{r}
#read in the data
damages <- read_csv(here("data","damages.csv")) %>% 
  clean_names()

warming <- read_csv(here("data","warming.csv")) %>%
  clean_names()
```

# Question 1: 

Using damages.csv, estimate a quadratic damage function relating the dollar 
value of damages to the change in global mean temperature. Estimate a model with a 
zero intercept because damages by construction must equal zero when there is no 
climate change. Plot your estimated damage function, overlaid with a scatterplot of
the underlying data.

```{r}
damage_climatechange <- lm(damages ~ warming +
                         I(warming^2)-1, # I value creates a mathmateical thing. (from sandy)
                       data = damages)

damage_predicted <- damage_climatechange$fitted.values
```

```{r}
# plot it
ggplot(damage_climatechange, aes(warming, damages)) +
  geom_line(aes(y = damage_predicted)) + 
  geom_point() +
  labs(title = "Monetary Damages due to Changes in Global Mean Temperature", x = "Amount of Warming (Celsius)", y = "Monetary Damages") + 
  theme_light() + 
  theme(plot.title = element_text(hjust = 0.5))
```

# Question 2

Use warming.csv and your estimated damage function to predict damages in each year 
under the baseline climate and the pulse scenario. Make four plots: (1) damages 
over time without the pulse, (2) damages over time with the pulse, (3) the 
difference in damages over time that arises from the pulse, and (4) the difference 
in damages over time from the pulse per ton of CO2 (you can assume that each ton of
the pulse causes the same amount of damage).

```{r}
# create a new tibble (tibble function creates a new dataset)
baseline = tibble(warming = warming$warming_baseline)

predicted_baseline = predict(damage_climatechange, newdata = baseline) # predict model from question 1. 

# plot predicted baseline against year

ggplot(predicted_baseline, aes(warming, year)) +
  geom_line(aes(y = ...)) + 
  geom_point() +
  labs(title = "", x = "", y = "") + 
  theme_light() + 
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
pulse = tibble(warming = warming$warming_pulse)

predicted_baseline
```


Notes from Sandy:
Question 1 asks:
With the warming how much damage is there?

Question 2 asks:
We are given the warming under the pulse and no pulse scenario (baseline). 
We use question 1 to predict the damages under the pulse and no pulse scenario.
Step 1- create a new tibble
baseline

When I increase






